Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-08 paper.tex
piccole correzioni

\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time.\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}

>>>>

\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time\footnote{We used an Intel(R) Xeon(R) CPU E5-2680 2.70GHz, 256GB (RAM).}.
